tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-03-17 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_berghei_pir_DESEQ.Rmd
Updated stats Rmd files & removed Cooks distance cut off for PBANKA_0600031 analysis

Notes:
* Would be worth looking at http://bioconductor.org/packages/release/bioc/vignettes/DESeq2/inst/doc/DESeq2.html#levels-without-samples to see if we can incorporate the experiment values into this too.

@@

# Change options so that numbers are displayed with all the zeros (e,g, as 1000000 not 1e6)
options(scipen = 999) 
```

@@

```{r read_count_data}
berg_counts <- read_xlsx('Manuscript_Frontiers_Counts_UpdatedNames.xlsx')

@@

```{r}
coef <- "stage_Liv.Meroz_vs_Asex.Mixed"
dds.deseq.livMeroz_v_asexMixed.lfcShr <- lfcShrink(dds.deseq, 
                                                  coef = coef,
                                                  type = "apeglm")

livMeroz_v_asexMixed_df <- as.data.frame(
  dds.deseq.livMeroz_v_asexMixed.lfcShr[rownames(dds.deseq.gamMale_v_asexMixed.lfcShr) %in% c('PBANKA_0100500','PBANKA_0600031'),]) %>%  
  mutate(contrast = coef)
```

@@

```{r}
coef <- "stage_Liv.Meroz_vs_Gam.Male"
dds.maleGam.deseq.livMeroz_v_gamMale.lfcShr <- lfcShrink(dds.maleGam.deseq, 
                                                         coef = coef,
                                                         type = "apeglm")

livMeroz_v_gamMale_df <- as.data.frame(
  dds.maleGam.deseq.livMeroz_v_gamMale.lfcShr[rownames(dds.maleGam.deseq.livMeroz_v_gamMale.lfcShr) %in% c('PBANKA_0317181',
                                                                                                           'PBANKA_0100500',
                                                                                                           'PBANKA_0600031'),]) %>%  
  mutate(contrast = coef)
```

>>>>

Notes:
* Have to remove Cook's distance cut off when looking at gene PBANKA_0600031 because otherwise DESEQ says that it is an outlier, from the data itself I'm not sure if I agree.

Future:
* Would be worth looking at http://bioconductor.org/packages/release/bioc/vignettes/DESeq2/inst/doc/DESeq2.html#levels-without-samples to see if we can incorporate the experiment values into this too.

@@

# Change options so that numbers are displayed with all the zeros (e,g, as 1000000 not 1e6)
options(scipen = 999)

set.seed(8)
```

@@

```{r read_count_data}
berg_counts <- read_xlsx('Manuscript_Frontiers_suppinfo_bergheiCounts_UpdatedNames.xlsx')

@@

```{r}
coef <- "stage_Liv.Meroz_vs_Asex.Mixed"
res <- results(dds.deseq,
               name = 'stage_Liv.Meroz_vs_Asex.Mixed',
               cooksCutoff = FALSE)
dds.deseq.livMeroz_v_asexMixed.lfcShr <- lfcShrink(dds.deseq, 
                                                  coef = coef,
                                                  res = res,
                                                  type = "apeglm")

livMeroz_v_asexMixed_df <- as.data.frame(
  dds.deseq.livMeroz_v_asexMixed.lfcShr[rownames(dds.deseq.gamMale_v_asexMixed.lfcShr) %in% c('PBANKA_0100500',
                                                                                              'PBANKA_0600031'),]) %>%  
  mutate(contrast = coef)
```

@@

```{r}
coef <- "stage_Liv.Meroz_vs_Gam.Male"
res <- results(dds.maleGam.deseq,
               name = 'stage_Liv.Meroz_vs_Gam.Male',
               cooksCutoff = FALSE)
dds.maleGam.deseq.livMeroz_v_gamMale.lfcShr <- lfcShrink(dds.maleGam.deseq, 
                                                         coef = coef,
                                                         res= res,
                                                         type = "apeglm")

(livMeroz_v_gamMale_df <- as.data.frame(
  dds.maleGam.deseq.livMeroz_v_gamMale.lfcShr[rownames(dds.maleGam.deseq.livMeroz_v_gamMale.lfcShr) %in% c('PBANKA_0317181',
                                                                                                           'PBANKA_0100500',
                                                                                                           'PBANKA_0600031'),]
  ) %>%  
  mutate(contrast = coef))
```

### 2021-03-17 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Updated stats Rmd files & removed Cooks distance cut off for PBANKA_0600031 analysis

# Change options so that numbers are displayed with all the zeros (e,g, as 1000000 not 1e6)
options(scipen = 999) 
```

@@

Download the data, and remove heterogeneous life cycle stages like 'Gam' and 'BldMl'. Will keep Asex.Mixed since we want to be able to compare that to other stages, although for each Asex stage we should remove the individual stages (like Rings) when looking at mixed, and the Mixed stages when looking at the inidvidual stages.

Initially I used counts here but I don't know if I made that up or not... Going to try with log(TPM+1).

```{r read_count_data}
# berg_counts <- read_xlsx('Manuscript_Frontiers_Counts_UpdatedNames.xlsx')

@@

```{r binom_glm}
berghei_tpm <- read_xlsx('Manuscript_Frontiers_SuppInfo_berghei.xlsx',
                      sheet = 2) %>% 
  melt(value.name = 'tpm', 
       variable.name = 'stage') %>% 
  mutate(experiment = as.factor(
    str_extract(stage, 
                pattern = '^Expt[[:digit:]]{2}')
    ),
stage = as.factor(
  str_extract(stage, 
              pattern = '(?<=Expt[[:digit:]]{2}_).+(?=_[[:digit:]]{1,2})')
  ),
Geneid = as.factor(Geneid),
tpm = as.factor(tpm)
)

>>>>

# Change options so that numbers are displayed with all the zeros (e,g, as 1000000 not 1e6)
options(scipen = 999)

set.seed(89)
```

@@

Download the data, and remove heterogeneous life cycle stages like 'Gam' and 'BldMl'. Will keep Asex.Mixed since we want to be able to compare that to other stages, although for each Asex stage we should remove the individual stages (like Rings) when looking at mixed, and the Mixed stages when looking at the individual stages.

```{r read_count_data}

@@
